\LARGE Performance Evaluation of Xenomai 3

### 2015-10-21 paper.tex
work on the conclusion

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance. However, our results show some of the unexpected slowdown of Xenomai 3 comparing to Xenomai 2.

>>>>

The Linux kernel running under Xenomai 3 can be PREEMPT\_RT as well, which means Linux ROOT gets currently running thread's priority through the native option of Xenomai 3 for maximum API/ABI compatibility in real-time environments. For the tight latency requirements such as real-time networking, Xenomai 3 allows to switch to dual kernel configurations utilizing I-pipe for maximum real-time performance, which brings sligtly better performance than Xenomai 2. However, comparing to Xenomai 2, our results show the unexpected slowdown of timer-irq latency in stressed condition while Xenomai 3 was configured as the dual kernel configuration of Xenomai 3 though. From our performance evaluation, Xenomai 3 is known as the most flexible real-time option.
